Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-18 WRITEUP/diff.tex
update markup to other colors to be less intimidating

% -------------------------------------- Final Edit Markup ----------------------------------
\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
\newcommand{\old}[1]{\textcolor{airforceblue}{\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
% -----------------------------------------------------------------------------------------------

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\new{The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
\input{table_obsprop}}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, \old{confirming the redshift at $z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.} \new{enabling us to constrain its redshift at
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to
the de-lensed spectrum, which is shown in \Fig{delensed}.
% instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our
% redshift determination of the dynamical center due to differential lensing (see \Sec{differential}).
}}. \old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms} \new{20.3\,$\pm$\,0.6 Jy \kms}. % see 15May16/

@@

\old{
Similar to previous studies of RXJ1131, where
differential lensing across the {\it HST}
$V$-, $I$-, and $H$-bands has been detected with a
magnification factor decreasing from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}},
the highly asymmetric \mbox{\bco} line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component.
This can be explained by the difference in magnification factor \mbox{$(\mu_{\rm L})$} which
varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
\new{\protect{Previous studies of RXJ1131 find evidence for differential lensing across
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
Here, we find that the highly asymmetric \bco line profile is predominantly a result of
differential lensing, where the redshifted emission is apparently much brighter than the
blueshifted component, as indicated by the difference in their magnification factor $(\mu_{\rm L})$, which
varies from 8.7 to 3.1 across the \bco line (\Tab{model}).
A secondary effect contributing to the asymmetry is caused by
the CO emission in the companion in the redshifted velocity channels.}}
The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
% The difference in magnification factors between CO and optical-to-NIR
% may further indicate that the CO emitting region is more extended and/or
% has a spatial offset from the optical-to-NIR emission
% (\ie different positions and alignment relative to the caustics) given
% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5)
% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and
% the degeneracy between the intrinsic source size and the magnification factor.

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion} \label{sec:diss}
\new{The properties of RXJ1131 and the companion derived in this section are summarized in \Tab{prop}.
\input{table_propRXJ}}

@@

\citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
The first set of lines is at $z$\ssim\old{0.653}\new{0.654}, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
the \mgii emission line.
Using the CO line center redshift as the systemic redshift,
we find that the redshift of the first set is fully consistent with the \old{systematic} \new{systemic} redshift. This
supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
are good proxies
to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
\old{On the other hand, the second set of lines is blueshifted by $\sim$780\,\kms, indicating that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.}
\new{On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.}
\old{One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
the central AGN, whereas this condition is not necessary for NLRs.
From an SDSS sample of $>$3800 quasars, \mbox{\citet{Richards02a}} find a}
\new{Offset between BLR and NLR lines have been reported in literature, e.g., 
\citet{Richards02a} find a}
 median of 97\kms and a dispersion of \mbox{269\,\kms} in the distribution of
\old{the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
that large offsets are uncommon. Nevertheless,
offsets as large as \mbox{$\sim$\,500\,\kms} have been observed in some cases.}
\new{the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in an SDSS sample of $>$3800 quasars, 
and \mbox{\citet{Bonning07a}} find a mean offset of \mbox{100\,\kms} with a dispersion of \mbox{212\,\kms} %FWHM = 500
between the broad component of
\mbox{H$\beta$ and [O\,{\scriptsize III}]} lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
illustrating that large offsets (\mbox{$\Delta v$$\gtrsim$\,500\,\kms}) are uncommon but have been observed in some cases.}

\new{Common interpretations invoked to explain offsets between BLR and systemic redshifts include
e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing angle towards the accretion disk, 
inclination effect, in which clumps in the accretion disk may block emission towards the far side of the disk, and thus the observed BLR emission is only
originating from
the redshifted inflowing gas component in the near side of the accretion disk of RXJ1131.
In the latter, \citet{Sluse07a} report a covering factor of 20\% based on \mgii absorption line at $z$\eq0.654.
Additionally, differentially lensing of the compact BLR emission by microlensing in RXJ1131\citep[\eg][]{Sluse07a, Sluse12a} 
may have boosted the redshifted component more than the blueshifted component,
thereby biasing the BLR line centroids towards longer wavelengths.}
{\bf DR: is it because of the large linewidth (one component of \mgii is $>$20000\kms, and broad comp. of H$\beta$ is $\sim$2000$-$4000\kms) that the referee thinks it's more likely to be inflow and therefore doesn't like the recoil black hole?
Sluse07:
"Another remarkable result is the presence in our spectra of a \mgii absorption doublet blueshifted at $z$\eq0.654. 
According to its velocity shift ($\Delta v$\ssim$-$660\,\kms). 
These lines disappear from the spectrum ratios A/B and C/B. This indicates that the absorbed flux is proportional to the flux coming from the continuum+BLR. This implies that the region at the origin of the absorption must cover both the continuum and the BLRs and that, within the uncertainties, their depths are identical in the spectra of the three images A, B, and C."
ok.. so is it because of this broad absorption component of \mgii that is at the same $z$ as the NLR lines, and therefore implying that the BLR and 
the AGN is not really spatially and kinematically offset, 
but the offset is truly just a manifestation of a rotating disk + other kinematics (+ absorption of continuum by BLR moving towards us, redshfiting the line centroid, + inflow of material + clumps blocking the far side inflow?)
}

>>>>

% -------------------------------------- Final Edit Markup ----------------------------------
\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{blue}{\uwave{#1}}}
\newcommand{\old}[1]{\textcolor{red}{\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
% -----------------------------------------------------------------------------------------------

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\new{The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.}
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, \old{confirming the redshift at $z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.} \new{enabling us to constrain its redshift at
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to
the de-lensed spectrum, which is shown in \Fig{delensed}}.}}
\old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
with a highly asymmetric double-horned line profile
as shown in \mbox{\Fig{CO21spec}}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms} \new{20.3\,$\pm$\,0.6 Jy \kms}. % see 15May16/

@@

\old{
Similar to previous studies of RXJ1131, where
differential lensing across the {\it HST}
$V$-, $I$-, and $H$-bands has been detected with a
magnification factor decreasing from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}},
the highly asymmetric \mbox{\bco} line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component.
This can be explained by the difference in magnification factor \mbox{$(\mu_{\rm L})$} which
varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
\new{Previous studies of RXJ1131 find evidence for differential lensing across
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
Here, we find that the highly asymmetric \mbox{\bco} line profile is predominantly a result of
differential lensing, where the redshifted emission is apparently much brighter than the
blueshifted component, as indicated by the difference in their magnification factor $(\mu_{\rm L})$, which
varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model})}.
A secondary effect contributing to the asymmetry is caused by
the CO emission in the companion in the redshifted velocity channels.}
The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
% The difference in magnification factors between CO and optical-to-NIR
% may further indicate that the CO emitting region is more extended and/or
% has a spatial offset from the optical-to-NIR emission
% (\ie different positions and alignment relative to the caustics) given
% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5)
% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and
% the degeneracy between the intrinsic source size and the magnification factor.

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion} \label{sec:diss}
\new{The properties of RXJ1131 and the companion derived in this section are summarized in \Tab{prop}}.
\input{table_propRXJ}

@@

\citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
The first set of lines is at $z$\ssim\old{0.653}\new{0.654}, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
the \mgii emission line.
Using the CO line center redshift as the systemic redshift,
we find that the redshift of the first set is fully consistent with the \old{systematic} \new{systemic} redshift. This
supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
are good proxies
to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
\old{On the other hand, the second set of lines is blueshifted by $\sim$780\,\kms, indicating that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.}
\new{On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.}
\old{One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
the central AGN, whereas this condition is not necessary for NLRs.
From an SDSS sample of $>$3800 quasars, \mbox{\citet{Richards02a}} find a}
\new{Offset between BLR and NLR lines have been reported in literature, e.g., 
\mbox{\citet{Richards02a}} find a}
 median of 97\kms and a dispersion of \mbox{269\,\kms} in the distribution of
\old{the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
that large offsets are uncommon. Nevertheless,
offsets as large as \mbox{$\sim$\,500\,\kms} have been observed in some cases.}
\new{the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in an SDSS sample of $>$3800 quasars, 
and \mbox{\citet{Bonning07a}} find a mean offset of \mbox{100\,\kms} with a dispersion of \mbox{212\,\kms} %FWHM = 500
between the broad component of
\mbox{H$\beta$ and [O\,{\scriptsize III}]} lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
illustrating that large offsets (\mbox{$\Delta v$$\gtrsim$\,500\,\kms}) are uncommon but have been observed in some cases.}

\new{Common interpretations invoked to explain offsets between BLR and systemic redshifts include
e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing angle towards the accretion disk, 
inclination effect, in which clumps in the accretion disk may block emission towards the far side of the disk, and thus the observed BLR emission is only
originating from
the redshifted inflowing gas component in the near side of the accretion disk of RXJ1131.
In the latter, \mbox{\citet{Sluse07a}} report a covering factor of 20\% based on \mbox{\mgii} absorption line at $z$\eq0.654.
Additionally, differentially lensing of the compact BLR emission by microlensing in RXJ1131 \mbox{\citep[\eg][]{Sluse07a, Sluse12a}}
may have boosted the redshifted component more than the blueshifted component,
thereby biasing the BLR line centroids towards longer wavelengths.}
{\bf DR: is it because of the large linewidth (one component of \mgii is $>$20000\kms, and broad comp. of H$\beta$ is $\sim$2000$-$4000\kms) that the referee thinks it's more likely to be inflow and therefore doesn't like the recoil black hole?
Sluse07:
"Another remarkable result is the presence in our spectra of a \mgii absorption doublet blueshifted at $z$\eq0.654. 
According to its velocity shift ($\Delta v$\ssim$-$660\,\kms). 
These lines disappear from the spectrum ratios A/B and C/B. This indicates that the absorbed flux is proportional to the flux coming from the continuum+BLR. This implies that the region at the origin of the absorption must cover both the continuum and the BLRs and that, within the uncertainties, their depths are identical in the spectra of the three images A, B, and C."
ok.. so is it because of this broad absorption component of \mgii that is at the same $z$ as the NLR lines, and therefore implying that the BLR and 
the AGN is not really spatially and kinematically offset, 
but the offset is truly just a manifestation of a rotating disk + other kinematics (+ absorption of continuum by BLR moving towards us, redshfiting the line centroid, + inflow of material + clumps blocking the far side inflow?)
}
